Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-11 Chapter-1/1-Theory.tex
s

Experimental results on several nuclei are reported in Figure as from \cite{}.

>>>>

Experimental results on several nuclei are reported in Figure as from \cite{PhysRevC.14.635}.

\begin{figure}[hbpt]
\centering
\includegraphics[]{Chapter-1/Images/PionsOnNuclei.png}
\caption{Pion-nucleus total cross sections:  $\sigma_{\pi^+}$ for positive pions (right) and $\sigma_{AV}$ (left) for the average between positive and negative pions $\sigma_{AV} = \frac{\sigma_{\pi^+} + \sigma_{\pi^-}}{2}$  in  the $\Delta$ resonance region.  The error bars include estimates of systematic uncertainties. The curves are the results of fits to the data assuming a Breit-Wigner shape. This summary plot  is reported in \cite{PhysRevC.14.635} and uses data from \cite{Clough1974, Wilkin:1973xd}.
}
\end{figure}
